### 2010-12-29 docs/slides/result.tex
Some slides added.

	\begin{table}[H]
	\centering
	\begin{tiny}
	\begin{spacing}{1.5}	
	\begin{tabular}{|l|l|c|c|l|c|}
	  \hline
	   														&\multicolumn{3}{c|}{Prey configuration} 																	
	   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
	  \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule110}} & \textbf{150 \(\uparrow\)} & \multicolumn{2}{c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
	  					 									& Rule30 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule30}}  	 & \textbf{150 \(\uparrow\)} & \multicolumn{2}{c|}{}\\ \cline{2-4}
	  					 									& Rule55 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule55}}  & \textbf{150 \(\uparrow\)} & \multicolumn{2}{c|}{}\\ \cline{2-4}
	  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule190}}& \textbf{150 \(\uparrow\)} & \multicolumn{2}{c|}{}\\ \hline
	  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
	  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{\textbf{2500 \(\uparrow\)}} \\ \hline
	  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
	  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
	  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{\textbf{7000 \(\uparrow\)}} \\ \hline
	  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
	  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 4 \\ \cline{5-6}
	   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
	\end{tabular}
	\end{spacing}	
	\end{tiny}
	\caption{Agent configuration of 4 prey species with increased population}
	\label{tab:config-table-4-more-prey}
	\end{table}

>>>>

	\begin{table}[H]
	\centering
	\begin{tiny}
	\begin{spacing}{1.5}	
	\begin{tabular}{|l|l|c|c|l|c|}
	  \hline
	   														&\multicolumn{3}{c|}{Prey configuration} 																	
	   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
	  \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule110}} & \textbf{150 \(\uparrow\)} & \multicolumn{2}{c|}{\multirow{4}{*}{\textbf{20 \(\uparrow\)}}} \\ \cline{2-4}
	  					 									& Rule30 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule30}}  	 & \textbf{150 \(\uparrow\)} & \multicolumn{2}{c|}{}\\ \cline{2-4}
	  					 									& Rule55 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule55}}  & \textbf{150 \(\uparrow\)} & \multicolumn{2}{c|}{}\\ \cline{2-4}
	  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule190}}& \textbf{150 \(\uparrow\)} & \multicolumn{2}{c|}{}\\ \hline
	  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
	  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{\textbf{2500 \(\uparrow\)}} \\ \hline
	  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
	  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
	  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{\textbf{7000 \(\uparrow\)}} \\ \hline
	  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
	  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 4 \\ \cline{5-6}
	   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
	\end{tabular}
	\end{spacing}	
	\end{tiny}
	\caption{Agent configuration of 4 prey species with increased population}
	\label{tab:config-table-4-more-prey}
	\end{table}
